---
format:
  revealjs:
    theme: default
    embed-resources: true
    slide-number: true
    navigation-mode: linear
    controls: true
---

# Rendering {background-color="#FFCD00"}

# Output Formats

Quarto provides the following output formats:

- HTML

- PDF

- MS Word (`docx`)

- OpenOffice (`odt`)

- ePub

## How To Render 

Rendering can be done in various ways:

**RStudio**: 

- Clicking the _Render_ button.

- Using the `quarto` R package:

```{r}
#| eval: false
#| echo: true
library(quarto)
quarto_render("my-reproducible-manuscript.qmd") # defaults to html
quarto_render("my-reproducible-manuscript", output_format = "pdf")
```

**Terminal**: Via the `quarto render` command and `--to` flag to specify output format.

```
quarto render my-reproducible-manuscript.qmd # defaults to html
quarto render my-reproducible-manuscript.qmd --to pdf
quarto render my-reproducible-manuscript.qmd --to docx
```

## Rendering to Multiple Formats 

Time to adapt the YAML metadata! 

```{yaml}
#| eval: false
#| echo: true
---
title: "My Reproducible Manuscript"
format: 
  html: default
  docx: default
  pdf: default
---
```

Then:

```{r}
#| eval: false
#| echo: true
library(quarto)
quarto_render("my-reproducible-manuscript.qmd")
```

OR

```
quarto render my-reproducible-manuscript.qmd
```

This means you don't have to run separate commands and specify the desired format with the `--to` flag everytime. **Note:** the _Render_ button will not work for multiple formats.

## Journal Formats

In addition to the default `html`/`pdf`/`docx` templates, Quarto offers a number of Journal templates. Currently, this includes:

- `acm`: Association of Computing Machinery (ACM)
- `plos`: Public Library of Science (PLOS) 
- `agu`: American Geophysical Union (AGU) 
- `elsevier`: Elsevier 
- `biophysical-journal`: Biophysical 
- `acs`: American Chemical Society (ACS) 
- `jss`: Journal of Statistical Software (JSS)

Previews of the templates are available on the [Quarto Documentation: Journals](https://quarto.org/docs/journals/) page. Keep an eye out for new templates!

## Journal Formats

You can utilize a journal template by running the following command:

`quarto use template quarto-journals/<template-name>`

For example,

`quarto use template quarto-journals/plos`

This command will create a new Quarto document, it would be best to use it at the beginning of your project.

## Exercise

1. Render your Quarto document to `docx` using both:

- the `quarto` R package
- the _Terminal_

2. Adjust the YAML to include both `html` & `docx` and re-render the document.

```{r}
library(countdown)

countdown(minutes = 10,
          color_background = "#FFCD00")
```


OPTIONAL:

3. Render your Quarto document to `pdf`.

4. Try out the PLOS Journal Template.

- simply obtain the template and render it, no need to make changes to the content.