---
format:
  revealjs:
    theme: default
    embed-resources: true
    slide-number: true
    navigation-mode: linear
    controls: true
---

# Rendering {background-color="#FFCD00"}

# Output Formats

Quarto provides the following output formats:

- HTML

- PDF

- MS Word (`docx`)

- OpenOffice (`odt`)

- ePub

## How To Render 

**1. In RStudio**: 

Click the _Render_ button OR use the `quarto` R package:

```{r}
#| eval: false
#| echo: true
library(quarto)
quarto_render("my-reproducible-manuscript.qmd") # defaults to html
quarto_render("my-reproducible-manuscript.qmd", output_format = "pdf")
```
  
<br>

**2. Terminal**: `quarto render` (`--to [output format]`)

```{bash}
#| eval: false
#| echo: true
quarto render
quarto render my-reproducible-manuscript.qmd # defaults to html
quarto render my-reproducible-manuscript.qmd --to pdf
```

## Rendering to Multiple Formats 

```{yaml}
#| eval: false
#| echo: true
---
title: "My Reproducible Manuscript"
format: 
  html: default
  docx: default
  pdf: default
---
```

Then:

```{r}
#| eval: false
#| echo: true
library(quarto)
quarto_render("my-reproducible-manuscript.qmd")
```

OR

```{bash}
#| eval: false
#| echo: true
quarto render my-reproducible-manuscript.qmd
```

You don't have to run separate commands with the `--to` flag.

**Note:** the _Render_ button will not work for multiple formats.

## Journal Formats

Besides default `html`/`pdf`/`docx`, Quarto offers journal templates. 
See also [Quarto Documentation: Journals](https://quarto.org/docs/journals/).

- `acm`: Association of Computing Machinery (ACM)
- `plos`: Public Library of Science (PLOS) 
- `agu`: American Geophysical Union (AGU) 
- `elsevier`: Elsevier 
- `biophysical-journal`: Biophysical 
- `acs`: American Chemical Society (ACS) 
- `jss`: Journal of Statistical Software (JSS)

## Journal Formats

Use a journal template **from the start of your project** (will create a new document):

```{bash}
#| eval: false
#| echo: true
quarto use template quarto-journals/<template-name>
```

<br>

For example:

```{bash}
#| eval: false
#| echo: true
quarto use template quarto-journals/plos
```

## Exercise

Go to the _Rendering_ chapter in the workshop book and refer to the instructions in the _Exercise_ section.

You will render your document into html and docx formats.

```{r}
library(countdown)

countdown(minutes = 10,
          color_background = "#FFCD00")
```
