# Getting Started {.unnumbered}

**1. Create a project in RStudio or VSCode**

- In RStudio, click File -> New Project -> New Directory -> New Project. 

- Give your project directory a clear name, preferably without spaces.

- Make sure your project directory folder is created (as a subdirectory) in an accessible place on your system.

- Select `Open project in a new session`.

**2. Create a project structure suited for reproducible work**

- You can generate a directory structure by running the following piece of code in you R console:

This is RSTudio:

```{r}
#| eval: false

dir.create("data", recursive = TRUE)
dir.create("docs", recursive = TRUE)
dir.create("results", recursive = TRUE)
dir.create("R", recursive = TRUE)

library(usethis)

usethis::use_readme_md(open = rlang::is_interactive())
usethis::use_mit_license(copyright_holder = NULL)
```

**3. Place your data in the correct folder**

```{r}
#| eval: false

library(palmerpenguins)

write.csv(palmerpenguins::penguins_raw, "data/data.csv")
```

**4. Create a R Markdown document for your manuscript.**

- In RStudio, click File -> New File -> R Markdown

- Click on 'From Template' and scroll through the available options and select the **MDPI Journal Article**

- Name the directory for this document (and associated files) as `manuscript` and ensure that it will be located in the `docs` folder.

**5. Familiarize yourself with the R Markdown document and associated files**

- YAML Header
- Sections
- Bibliography 