# Getting Started {.unnumbered}

::: {.panel-tabset}

## R

**1. Create a Project in RStudio**

- In RStudio, click _File_ -> _New Project_ -> _New Directory_ -> _New Project_. 

- Give your project directory a clear name, without using spaces. For example, `my-reproducible-manuscript`.

- Make sure your project will be created (as a subdirectory) in an accessible place on your system.

- Check the _Open in new session_ option.

- Click _Create Project_.

**2. Structure your Project for reproducible work**

- Generate a directory structure by running the following piece of code in the _Console_ of RStudio:

```{r}
#| eval: false

dir.create("data", recursive = TRUE)
dir.create("docs", recursive = TRUE)
dir.create("results", recursive = TRUE)
dir.create("R", recursive = TRUE)

# install.packages("usethis")
library(usethis)

usethis::use_readme_md(open = rlang::is_interactive())
usethis::use_mit_license(copyright_holder = NULL)
```

**3. Get the data for your Project**

- Obtain the data and place it in the correct folder by running the following piece of code in the _Console_ of RStudio:

```{r}
#| eval: false

# install.packages("palmerpenguins")
library(palmerpenguins)

write.csv(palmerpenguins::penguins_raw, "data/data.csv")
```

**4. Create a Quarto document for your manuscript.**

- In RStudio, click _File_ -> _New File_ -> _Quarto Document_

- Give your document a Title, such as `My Reproducible Manuscript`.

- Deselect the _Use visual markdown editor_ option.

- Click _Create_.

**6. Render the Quarto document to HTML**

- Click the _Render_ button in the menu bar.

- Give the Quarto document a clear name, without using spaces. For example, `my-reproducible-manuscript`.

- Save the Quarto document in the `docs folder you recently created.

- Once everything has been saved correctly, click the _Render_ button in the menu bar again.

- The rendered, HTML copy of your document will appear in your web browser or alongside the editor in RStudio.

## Python



:::